---
title: "MainText_DDtransmission"
author: "Matthew Silk"
date: "21/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##An R script to simulate host-pathogen dynamics for a range of host life-history and demographic strategies and pathogen virulences and transmissibilities when pathogen transmission is density-dependent

***

####Load required R packages

```{r Packages}
library(boot)
```

***

####Define parameters

```{r Define_Parameters}

#Host survival
Sus<-seq(0.2,0.8,0.1)

#Host recruitment rate
Rs<-(1-Sus)/Sus

#Disease-induced mortality
phi<-seq(0,0.99,0.01)

#Disease-induced change in reproductive output
#not used in this model
psi<-1

#Beta (transmission probabilities)
betas<-seq(0.006,0.0095,0.0005)

#Required parameters density-dependent effect
#t sets the value for the stable uninfected host population size
t<-100
dd.effs<-c(0.00001,0.000025,0.00005,0.0001,0.00025,0.0005,0.001,0.0025,0.005,0.01)
r.adj<-1

```

***

####Run Model

The code saves results for each host life-history separately in the current working directory
Results files are:
1. Host population size for survival-based regulation
2. Host population size for reproduction-based regulation
3. Pathogen prevalence for survival-based regulation
4. Pathogen prevalence for reproduction-based regulation

```{r Define_Parameters}

#Loop over host life-history strategies
for(jjjj in 1:length(Sus)){

#Select current host life-history parameters
Su<-Sus[jjjj]
R<-Rs[jjjj]

#Set up array to store overall simulation results
dRESULTS.PR.R<-array(0,dim=c(length(betas),length(phi),length(dd.effs)))
dRESULTS.N.R<-array(0,dim=c(length(betas),length(phi),length(dd.effs)))
dRESULTS.PR.S<-array(0,dim=c(length(betas),length(phi),length(dd.effs)))
dRESULTS.N.S<-array(0,dim=c(length(betas),length(phi),length(dd.effs)))

#Loop over strengths of host density-dependence
for(jjj in 1:length(dd.effs)){
  
  #Select current strength of host density-dependence
  dd.eff<-dd.effs[jjj]
  
  #Set up matrices to store results
  t.results.pr.r<-matrix(0,nr=length(betas),nc=length(phi))
  t.results.n.r<-matrix(0,nr=length(betas),nc=length(phi))
  t.results.pr.s<-matrix(0,nr=length(betas),nc=length(phi))
  t.results.n.s<-matrix(0,nr=length(betas),nc=length(phi))
  
  #Loop over pathogen transmissibilities
  for(jj in 1:length(betas)){
    
    beta<-betas[jj]
    
    #Set up vectors to store individual simulation results
    prev.R<-array(0,length(phi))
    prev.S<-array(0,length(phi))
    N.R<-array(0,length(phi))
    N.S<-array(0,length(phi))
    
    #Loop over values for disease-induced mortality
    for(j in 1:length(phi)){
      
      #Start individual simulation run
      #X.R stores results for density-dependent recruitment of hosts
      #X.S for density-dependent survival of hosts
      #Start with 50 uninfected and 50 infected hosts
      x.R<-array(0,dim=c(3,100000))
      x.R[1:2,1]<-c(50,50)
      x.R[3,1]<-sum(x.R[1:2,1])
      x.S<-array(0,dim=c(3,100000))
      x.S[1:2,1]<-c(50,50)
      x.S[3,1]<-sum(x.S[1:2,1])
      
      for(i in 2:dim(x.R)[2]){
        
        tmp.r<-R-r.adj*(dd.eff*(x.R[3,i-1]-t))
        if(tmp.r<0.00001){tmp.r<-0.00001}
        tmp.su<-Su-dd.eff*(x.S[3,i-1]-t)
        if(tmp.su>0.99999){tmp.su<-0.99999}
        if(tmp.su<0.00001){tmp.su<-0.00001}
        
        #Host DD recruitment model
        x.R[1,i]<-Su*(1-beta*(x.R[2,i-1]))*x.R[1,i-1]+
          Su*tmp.r*(1-beta*(x.R[2,i-1]))*x.R[1,i-1]+
          Su*phi[j]*tmp.r*psi*(1-beta*(x.R[2,i-1]))*x.R[2,i-1]
        x.R[2,i]<-Su*beta*(x.R[2,i-1])*x.R[1,i-1]+
          Su*tmp.r*(beta*(x.R[2,i-1]))*x.R[1,i-1]+
          Su*phi[j]*x.R[2,i-1]+
          Su*phi[j]*tmp.r*psi*(beta*(x.R[2,i-1]))*x.R[2,i-1]
        x.R[3,i]<-sum(x.R[1:2,i])
        
        #Host DD survival model
        x.S[1,i]<-tmp.su*(1-beta*(x.S[2,i-1]))*x.S[1,i-1]+
          tmp.su*R*(1-beta*(x.S[2,i-1]))*x.S[1,i-1]+
          tmp.su*phi[j]*R*psi*(1-beta*(x.S[2,i-1]))*x.S[2,i-1]
        x.S[2,i]<-tmp.su*beta*(x.S[2,i-1])*x.S[1,i-1]+
          tmp.su*R*(beta*(x.S[2,i-1]))*x.S[1,i-1]+
          tmp.su*phi[j]*x.S[2,i-1]+
          tmp.su*phi[j]*R*psi*(beta*(x.S[2,i-1]))*x.S[2,i-1]
        x.S[3,i]<-sum(x.S[1:2,i]) 
        
        if(is.na(x.S[1,i])){x.S[1,i]<-0}
        if(is.na(x.S[2,i])){x.S[2,i]<-0}
        if(is.na(x.S[3,i])){x.S[3,i]<-0}
        if(is.na(x.R[1,i])){x.R[1,i]<-0}
        if(is.na(x.R[2,i])){x.R[2,i]<-0}
        if(is.na(x.R[3,i])){x.R[3,i]<-0}
        
        
      } #end loop over timesteps
      
      #Store results
      prev.R[j]<-x.R[2,i]/x.R[3,i]
      prev.S[j]<-x.S[2,i]/x.S[3,i]
      N.R[j]<-x.R[3,i]
      N.S[j]<-x.S[3,i]
      
    } # end loop over phi
    
    #Store results
    t.results.pr.r[jj,]<-prev.R
    t.results.pr.s[jj,]<-prev.S
    t.results.n.r[jj,]<-N.R
    t.results.n.s[jj,]<-N.S
    
    
  } #end loop over Betas
  
  #Store results
  dRESULTS.PR.R[,,jjj]<-t.results.pr.r
  dRESULTS.PR.S[,,jjj]<-t.results.pr.s
  dRESULTS.N.R[,,jjj]<-t.results.n.r
  dRESULTS.N.S[,,jjj]<-t.results.n.s
  
  print(jjj) #print to update on code progress
  
} #end loop over host density-dependences

#Save results for each host life-history separately
#Results files are:
#1. Host population size for survival-based regulation
#2. Host population size for reproduction-based regulation
#3. Pathogen prevalence for survival-based regulation
#4. Pathogen prevalence for reproduction-based regulation
saveRDS(dRESULTS.N.S,paste0("MTdNS_",Su,".rds"))
saveRDS(dRESULTS.N.R,paste0("MTdNR_",Su,".rds"))
saveRDS(dRESULTS.PR.S,paste0("MTdPRS_",Su,".rds"))
saveRDS(dRESULTS.PR.R,paste0("MTdPRR_",Su,".rds"))

} #end loop over host life-histories

```

